\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\Large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeitem}[1]{
  \item\small{
    #1 \vspace{-2pt}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{#2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubheadingNew}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} \textbar{} \textit{\small#2} &  \textit{\small#3}\\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubSubheading}[1]{
    \hspace{0.2em}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1}
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{\textbullet}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubItemListStart}{\begin{itemize}[leftmargin=*,label={}]}
\newcommand{\resumeSubItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://dinhdat.com/}{\LARGE Vo Dinh Dat}} & Email : \href{mailto:vodinhdat03@gmail.com}{vodinhdat03@gmail.com}\\
%   \href{https://dinhdat.com/}{www.dinhdat.com} & Mobile : \href{tel:+84399565203}{+84-399-565-203} \\
%   & \href{https://www.linkedin.com/in/datvodinh/}{{LinkedIn: linkedin.com/in/datvodinh/}}
% \end{tabular*}

\begin{flushleft}
  \textbf{\huge {Dat Vo Dinh}} \\ \vspace{4pt}
  \hspace{6pt}{{Hanoi, Vietnam}} $|$ \href{tel:+84399565203}{{+84--399--565--203}} $|$ \href{https://dinhdat.com}{{www.dinhdat.com}}
  $|$ \href{https://github.com/datvodinh/}{{github.com/datvodinh}} $|$ \href{mailto:vodinhdat03@gmail.com}{{vodinhdat03@gmail.com}}
\end{flushleft}
% $|$ \href{https://linkedin.com/in/datvodinh}{{linkedin.com/in/datvodinh}}
%-----------SUMMARY-----------------
% \section{Summary}
% An ambitious junior with a year of experience in research and 

%-----------EDUCATION-----------------
\section{Educations}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Hanoi University of Science and Technology}{\textit{Hanoi, Vietnam}}
      {BSc in Data Science and Artificial Intelligience (DS-AI)}{Aug 2021 -- Aug 2025 (Expected)}
    % \resumeSubheading
    %   {Phan Boi Chau Gifted High School}{Nghe An, Vietnam}
    %   {Specialization in Mathematic;  GPA: 3.64 (9.1/10.0)}{Aug. 2018 -- July. 2021}
  \resumeSubHeadingListEnd

  %--------PROGRAMMING SKILLS------------
  
\section{Technical Skills}
\resumeItemListStart[leftmargin=*,label={}]
  \resumeitem{\textbf{Programming Languages}: {Python, SQL, Java, C++.}} \\[-\baselineskip]
  \resumeitem{\textbf{Deep Learning}: {Pytorch, Lightning, OpenCV, Transformers, Unsloth, Ollama, LlamaIndex.}} \\[-\baselineskip]
  \resumeitem{\textbf{Deployment and MLOps}: {Docker, Gradio, WandB, AzureML, AWS.}} \\[-\baselineskip]
  \resumeitem{\textbf{Backend and Tools}: {MongoDB, Chroma, Pydantic, FastAPI, Git/Github, Github Actions, Postman, Figma, Jira.}} \\[-\baselineskip]
\resumeItemListEnd


%-----------EXPERIENCE-----------------
\section{Experiences}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Freelance}{Taiwan}
      {Quantitative Researcher}{Oct 2023 -- Jan 2024}
      \resumeItemListStart
        \resumeitem{\textbf{Technologies:} Pytorch, Lightning, WandB, Transformers, Polars, Amazon S3}
        \resumeitem{Design and improve the reward function for the RL based trading environment to mimic real-world scenarios.}
        \resumeitem{Developing an RL agent combine with current SOTA algorithms such as Transformers, surpass the performance of traditional ensemble models such as XGBoost, Gradient Boosting,... through backtest evaluation.}
      \resumeItemListEnd
      

    \resumeSubheading
      {VIS (Startup)}{Hanoi, Vietnam}
      {Part Time AI Researcher}{May 2022 -- Jul 2023}
      \resumeItemListStart
        \resumeitem{\textbf{Technologies:} Pytorch, Numpy, Numba, Gynasium, Selenium.}
        \resumeitem{Researched and implemented 2 deep reinforcement learning algorithms, successfully surpass 95\% of the environments in the system by competing with other decision-making agents.}
        \resumeitem{Developed three gym-based multiplayer environments for researching algorithms, with optimization achieved using Numpy and Numba JIT, reaching the speed upto 1000 games per second.}
        \resumeitem{Research about Japanese stock market, crawl data from 3 different sources: Minkabu, MarketWatch and YahooJP and cross-check to ensure the credibility of sources.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart

\resumeSubheadingNew
    {Open source contributions}{Github}{2024}
    \resumeItemListStart
      \resumeitem{Ollama (60k stars): Add my Chatbot project to community integrations in the project's documents.}
      \resumeitem{LlamaIndex (30k stars): Fix a bug in fusion retriever module.}
      \resumeItemListEnd
    
  
\resumeSubheadingNew
    {LLM finetuning}{Transformers, Unsloth, PEFT, Trl}{Apr 2024}
    \resumeItemListStart
      \resumeitem{Finetune open sources LLM model such as Llama-3, Mistral to perform multiple task such as:}
      \resumeitem{Function calling: enable LLM to use external functions and tools provided to solve complex problems.}
      \resumeitem{Instruction tuned: helps the LLM follow instructions better to more reliably perform complex tasks and instructions.}
      \resumeitem{Structured output: LLM return structured output such as JSON, XML...based on user's input.}
    \resumeItemListEnd
    

  \resumeSubheadingNew
    {RAG chatbot}{Ollama, LlamaIndex, ChromaDB, Gradio, Docker, FastAPI, Ngrok}{Mar 2024}
    \resumeItemListStart
      \resumeitem{Build a fully local Chatbot with advanced RAG pipeline to give precise answers base on multiple given documents.}
      \resumeitem{Pull and use any open sources model from Huggingface and Ollama with different quantization.}
      \resumeitem{Design a simple web interface so users can customize LLM models and input documents to use the chatbot.}
      \resumeitem{Containerize all the chatbot system and service using Docker for deployment and management.}
      
    \resumeItemListEnd
    
  \resumeSubheadingNew
    {Stable Diffusion from scratch}{Pytorch, Lightning, WandB, Gradio}{Feb 2024}
    \resumeItemListStart
      \resumeitem{Implemented Latent Diffusion Model (Stable Diffusion) from scratch for education purpose.}
      \resumeitem{Implemented full training and tracking experiment pipeline, different sampling algorithms such as DDIM, PLMS...}
      \resumeitem{Build a simple UI with Gradio to visualize the inference process of the model with different sampling methods.}
    \resumeItemListEnd

  % \resumeSubheadingNew
  %   {Personal Website}{Javascript, HTML, CSS, Jekyll}{Jun 2023 -- Now}
  %   \resumeItemListStart
  %     \resumeitem{My personal blog to share my knowledge about AI, Machine Learning, showing step by step approach the model and implemented it from scratch.}
  %     \resumeitem{A landing page contain my contact information and my resume.}
  %   \resumeItemListEnd

  

\resumeSubHeadingListEnd


%-----------LANGUAGES-----------------
% \section{Languages}
%   \resumeSubHeadingListStart
%     \item{\textbf{Vietnamese}: Native language.}\\[-\baselineskip]
%     \item{\textbf{English}: Full professional proficiency.}\\[-\baselineskip]
%   \resumeSubHeadingListEnd
%--------------------------------------
\end{document}