%!TEX program = lualatex

\documentclass[letterpaper,11pt]{article}

\usepackage{fontspec}  % For custom fonts
\setmainfont{Arial}

% \usepackage{helvet}
% \renewcommand{\familydefault}{\sfdefault}  % Set Helvetica (Arial-like) as default font

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\setlength{\footskip}{4.08003pt}
\usepackage[english]{babel}
\usepackage{tabularx}
% \input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
% \titleformat{\section}{
%   \vspace{-4pt}\scshape\raggedright\large
% }{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

% \titleformat{\section}{
%   \vspace{-4pt}\raggedright\large
% }{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

\titleformat{\section}{
  \vspace{-4pt}\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-1pt}}
  }
}

\newcommand{\resumeitem}[1]{
  \item \small{
    % \setlength{\parsep}{2pt}
    % \setlength{\itemsep}{\parsep}
    \hspace{1pt} #1 \vspace{-1pt}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubheadingNew}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} \textbar{} \textit{\small#2} &  \textit{\small#3}\\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubSubheading}[1]{
    \hspace{0.2em}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1}
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{\textbullet}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubItemListStart}{\begin{itemize}[leftmargin=*,label={}]}
\newcommand{\resumeSubItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
  \textbf{\Huge {Dat Vo Dinh}} \\ \vspace{4pt}
  \hspace{6pt}{{Hanoi, Vietnam}} $|$ \href{tel:+84399565203}{{+84-399-565-203}} $|$ \href{https://dinhdat.com}{{dinhdat.com}}
  $|$ \href{https://github.com/datvodinh/}{{github.com/datvodinh}} $|$ \href{mailto:vodinhdat03@gmail.com}{{vodinhdat03@gmail.com}}
\end{center}

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Hanoi University of Science and Technology}{Aug 2021 -- Aug 2025 (Expected)}
    {BSc in Data Science and Artificial Intelligience - GPA 3.2/4.0}{\textit{Hanoi, Vietnam}}
\resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
  
\section{Technical Skills}
\resumeItemListStart[leftmargin=2pt,label={}]
  \resumeitem{\textbf{Programming Languages}: {Python, Javascript, Java, C++.}} \\[-\baselineskip]
  \resumeitem{\textbf{Deep Learning}: {Pytorch, Lightning, Ray, Ultralytics, Transformers, OpenCV, Spacy.}} \\[-\baselineskip]
  \resumeitem{\textbf{MLOps and Deployment}: {MLFlow, Kubeflow, Kuberay, WandB, Dagster, AWS, Docker, Kubernetes, Helm, FluxCD.}} \\[-\baselineskip]
  \resumeitem{\textbf{Fullstack Development}: {FastAPI, Jinja, Gradio, ReactJS, NextJS, TailwindCSS, HTML, CSS.}} \\[-\baselineskip]
  \resumeitem{\textbf{Developer Tools}: {Git, Github Actions, Jenkins, Pydantic, Poetry, Ruff, Prettier.}} \\[-\baselineskip]
\resumeItemListEnd

%-----------EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {AI Engineer}{Apr 2024 -- Now}
      {Contracting}{Australia}
      \resumeItemListStart
        \resumeitem{\textbf{Technologies:} Pytorch, Transformers, Ray, Dagster, Qdrant, FastAPI, Docker, Kubernetes, Kuberay, FluxCD.}
        \resumeitem{Build a distributed and scalable data pipeline using Dagster, capable of ingesting thousands of documents, images, and videos effectively.}
        \resumeitem{Develop and serve a robust and autoscale model orchestration with Ray Serve, enabling seamless inference across multiple models to process the ingested data.}
        \resumeitem{Design and implement a vector retrieval search engine and GUI, enhancing data retrieval with hybrid search and integrating visualization tools to display search results effectively.}
        % \resumeitem{Deploy the data pipeline and search engine on a Kubernetes cluster, utilizing FluxCD for efficient, scalable, and continuous deployment.}
      \resumeItemListEnd

    \resumeSubheading
      {Quantitative Researcher}{Sep 2023 -- Jan 2024}
      {Contracting}{Taiwan}
      \resumeItemListStart
        \resumeitem{\textbf{Technologies:} Pytorch, Lightning, WandB, Transformers, Polars, Amazon S3}
        \resumeitem{Design and improve the reward function for the RL based trading environment to mimic real-world scenarios.}
        \resumeitem{Developing an RL agent combine with current SOTA algorithms such as Transformers, surpass the performance of traditional ensemble models such as XGBoost, Gradient Boosting,... through backtest evaluation.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Part Time AI Researcher}{May 2022 -- Jul 2023}
      {VIS Startup}{Hanoi, Vietnam}
      \resumeItemListStart
        \resumeitem{\textbf{Technologies:} Pytorch, Numpy, Numba, Gynasium, Selenium.}
        \resumeitem{Research and implement 2 deep reinforcement learning algorithms, successfully surpass 95\% of the environments in the system by competing with other decision-making agents.}
        \resumeitem{Develop three gym-based multiplayer environments for researching algorithms, with optimization achieved using Numpy and Numba JIT, reaching the speed upto 1000 games per second.}
        \resumeitem{Research about Japanese stock market, crawl data from 3 different sources: Minkabu, MarketWatch and YahooJP and cross-check to ensure the credibility of sources.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Personal Projects}
\resumeItemListStart[leftmargin=2pt,label={}]
  \resumeitem{\textbf{Open Source contributions}: {Fix bug and contribute integration to Ollama (85k stars) and LlamaIndex (35k stars).}} \\[-\baselineskip]
  \resumeitem{\textbf{RAG Chatbot}: {Build and serve a chatbot application with advanced RAG pipeline and fully local LLM models.}} \\[-\baselineskip]
  \resumeitem{\textbf{Personal Website}: {A landing page with personal information and personal technical blog about AI/Deep Learning.}} \\[-\baselineskip]
  \resumeitem{\textbf{Stable Diffusion from scratch}: {Implemented Latent Diffusion Model from scratch for education purpose.}} \\[-\baselineskip]
  \resumeitem{\textbf{LLM finetuning}: {Finetune open sources LLM to perform downstream tasks such as function calling, summarizaiton...}} \\[-\baselineskip]
\resumeItemListEnd

\end{document}

